%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Canonical, Senior Design Manager (Infrastructure)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover-fira}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Marko Rosic}}{%
  \href{mailto:marko@rosic.net}{marko@rosic.net} | +381 60 585 44 55 | \urlstyle{same}\href{https://linkedin.com/in/markorosic}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Canonical hiring team,}

\lettercontent{I'm writing about the Senior Design Manager (Infrastructure)
role. I've spent 15 years building design teams, design systems, and the
practices that connect design to how engineering ships. Ubuntu is in the
stack of almost every product I've designed for. The challenge of making
cloud infrastructure tools genuinely usable for developers and cloud
engineers — people with precise mental models and no patience for UX
that gets in their way — is the kind of problem I want to tackle next.}

\lettercontent{My track record maps directly to what the role requires:}

{\raggedright\fontspec{Fira Sans}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
  \item \textbf{Design systems built end to end.} At Beyond Clicks I architected
        a full design system from scratch: token architecture, a
        Figma-variables-to-theme-tokens pipeline as a single source of
        truth, and a complete component library. At Gentoo Media and
        Catena Media I built company-wide systems that cut development
        time by 30\% and time-to-market by 25\%.
  \item \textbf{Teams of designers working on technical products.} I led a
        cross-functional team of seven including two team leads at Gentoo,
        and I've consistently managed designers whose work sits at the
        boundary between complex back-end systems and the interfaces that
        make them usable.
  \item \textbf{Technical tooling UX.} At Smith Micro I designed backend
        tooling for device management systems and an IoT notification
        service alongside carrier-branded Android apps, working directly
        with engineering to meet precise technical specifications.
  \item \textbf{Fully remote, EMEA, since day one.} I'm based in Belgrade and
        have worked in remote, async-first environments throughout my
        career. I use AI including Claude Code to build faster and
        contribute to open source tooling through Figma plugin
        development.
\end{itemize}\par}

\lettercontent{Canonical's distributed model and commitment to open source
are the kind of environment where I do my best work. I'm available in
the EMEA time zone and happy to travel up to four times a year for team
sprints. I would welcome the chance to talk about the Infrastructure
design team and the problems it's working through.}

\begin{flushright}
\closing{Kind regards,}
\signature{Marko Rosic}
\end{flushright}
\end{document}
