%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Deel, Lead Product Designer - Connectivity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Marko Rosić}}{  \href{mailto:marko@rosic.net}{marko@rosic.net} | +381 60 585 44 55 |  \urlstyle{same}\href{https://linkedin.com/in/markorosic}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Deel hiring team,}

\lettercontent{I am applying for the Lead Product Designer role on the Connectivity team. Platform design (API portals, partner integrations, white-label experiences, developer tooling) is where getting the design right is hardest. The users are technical, have strong opinions, and will notice immediately when something is wrong. I want to work on problems like that.}

\lettercontent{I work best where design meets engineering. I build Figma plugins, use Claude Code to make working prototypes, and stay close to how things are actually built. I lead small teams by doing the work alongside them. What I would bring to Connectivity:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Design systems for complex products:} I build token-based, multi-brand component libraries, with clear component contracts and handoff that engineers actually use. One of them cut development time by 30\% and ran across 10+ websites.
    \item \textbf{Technical interface experience:} Earlier in my career at Smith Micro I designed backend tooling for device management and an IoT notification system, working across consumer-facing UX and complex operational data views. That is my closest analogue to partner portals and integration tooling.
    \item \textbf{Engineering-boundary work:} I build Figma plugins and use Claude Code to prototype. I am comfortable in pull request reviews and technical discussions, not just handing off screens.
    \item \textbf{Team leadership by doing:} I led a team of seven including two team leads. I set the bar and ship the work alongside the team.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Deel is the company that makes global employment possible. The fact that I am based in Belgrade and applying to work remotely is something Deel exists to enable. I can start immediately, with no visa or relocation friction, in the same timezone as your European teams.}

\lettercontent{I would like to talk about the Connectivity team and what you are trying to build.}

\begin{flushright}
\closing{Kind regards,}

\signature{Marko Rosić}
\end{flushright}
\end{document}
