%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Dash0, Director of Design (EMEA Remote)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Marko Rosić}}{  \href{mailto:marko@rosic.net}{marko@rosic.net} | +381 60 585 44 55 |  \urlstyle{same}\href{https://linkedin.com/in/markorosic}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Dash0 hiring team,}

\lettercontent{I am applying for the Director of Design role. Observability tooling is a hard design problem: the people using it are engineers under pressure, the data is dense, and getting the interface wrong has real consequences. I want to work on problems like that.}

\lettercontent{I have spent 15 years building design systems and leading design teams in fast-moving product companies, and I work best where design meets engineering. What I would bring to Dash0:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Design systems:} I build token-based, multi-brand component libraries, with component contracts and handoff that engineers actually use. One of them cut development time by 30\% and later ran across 10+ websites.
    \item \textbf{Teams that run:} I have led a cross-functional design team of seven, including two team leads who each managed their own sub-team. I set the direction, remove blockers, and let people own their work.
    \item \textbf{Technical interfaces:} Earlier in my career I designed backend tooling for device management and an IoT notification system at Smith Micro, working across both consumer-facing UX and complex operational data views. That is the closest I have to your domain, and I know it is not the same as observability.
    \item \textbf{AI at the engineering boundary:} I use Claude Code to build working prototypes and Figma plugins, which keeps me close to how products are built and gives me a different view of what is technically straightforward versus hard.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Dash0 is a small team building something with serious engineering ambition. You are OpenTelemetry-native, backed by Accel and Balderton, and designing for an audience that will notice immediately if the product feels like it was designed by someone who does not understand their workflow. I do not have an observability background, but I have spent years building design infrastructure for technical, multi-market products, and I learn domain context quickly when I am embedded in the team.}

\lettercontent{I am based in Belgrade, which is CET, so I am in your timezone. I would like to talk about what you are building and what you need from a design lead.}

\begin{flushright}
\closing{Kind regards,}

\signature{Marko Rosić}
\end{flushright}
\end{document}
