%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Skyscanner, Director of Product Design (Barcelona)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Marko Rosić}}{  \href{mailto:marko@rosic.net}{marko@rosic.net} | +381 60 585 44 55 |  \urlstyle{same}\href{https://linkedin.com/in/markorosic}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Skyscanner hiring team,}

\lettercontent{I am applying for the Director of Product Design role in Barcelona. For more than 15 years I have led design for high-traffic, multi-market consumer websites, built the design systems and teams that keep the work consistent as products grow. Most recently I led a team of seven and the company-wide design system behind several brands.}

\lettercontent{What I would bring to this product area:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Design systems:} I build token-based, multi-brand component libraries, with handoff that engineers can actually use. One of them cut development time by 20\% and later ran across 10+ websites.
    \item \textbf{Design that moves the numbers:} changes to how we worked that cut time-to-market by 25\%, and a redesign that raised mobile traffic by 20\% and retention by 15\%.
    \item \textbf{Teams that grow:} I coach and manage design leads, set the standard for the work, and build teams that can run without constant escalation.
    \item \textbf{AI where design meets engineering:} I use Claude Code myself to build working prototypes and Figma plugins, and to learn how AI changes product design and the way teams work.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Skyscanner is the kind of company I want to work for: a travel platform used by about 160 million people a month in 52 countries, where good design has to hold up at scale. You are moving toward AI and conversational travel planning. That sits right where I work, between design and engineering, and multi-market consumer web is what I know best.}

\lettercontent{I come from a design-craft background, but I also have an economics degree and I am used to measuring design in customer and business terms. I am ready to relocate to Barcelona, and I would be glad to talk about how I can help raise the quality of design in your product area.}

\begin{flushright}
\closing{Kind regards,}

\signature{Marko Rosić}
\end{flushright}
\end{document}
