%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Almedia, Head of Product Design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover-fira}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Marko Rosic}}{%
  \href{mailto:marko@rosic.net}{marko@rosic.net} | +381 60 585 44 55 | \urlstyle{same}\href{https://linkedin.com/in/markorosic}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Almedia hiring team,}

\lettercontent{I'm applying for the Head of Product Design role. Almedia's
growth to 50 million users while staying bootstrapped tells me the product
earns its audience rather than buying it. Building the design capability
to match that scale — the systems, the standards, the team quality, and
the speed to keep up with the growth — is the work I find most
interesting.}

\lettercontent{I work hands-on. I don't direct from a distance; I design,
prototype, and build tooling alongside my team. My relevant experience:}

{\raggedright\fontspec{Fira Sans}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
  \item \textbf{End-to-end consumer product ownership.} Most recently as Head
        of Design for an international consumer platform: retention flows,
        onboarding, progressive filter architecture, and conversion
        optimisation on high-revenue surfaces. Same kind of product
        detail that drives performance on Freecash.
  \item \textbf{Design systems that reduce engineering friction.} I architected
        a full design system from token architecture through component
        library, cutting development time by 30\% and time-to-market by
        25\% at the companies I've led design for.
  \item \textbf{Small teams, high output.} I led a team of seven at Gentoo
        Media, including two team leads. I know how to run a lean design
        team with high expectations and keep the quality bar up.
  \item \textbf{Speed through tooling.} I build Figma plugins and use AI
        including Claude Code to ship UX and internal tooling faster,
        without sacrificing craft.
\end{itemize}\par}

\lettercontent{Being based in Belgrade, I would need a German work permit to
join the team in Berlin, and I'm raising this upfront so it's on the
table. I'm asking directly: is visa sponsorship something Almedia can
support for this hire? If so, I'd be glad to move the conversation
forward.}

\begin{flushright}
\closing{Kind regards,}
\signature{Marko Rosic}
\end{flushright}
\end{document}
