%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Deel, Lead Product Designer - Fintech
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover-fira}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Marko Rosić}}{  \href{mailto:marko@rosic.net}{marko@rosic.net} | +381 60 585 44 55 |  \urlstyle{same}\href{https://linkedin.com/in/markorosic}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Deel hiring team,}

\lettercontent{I am applying for the Lead Product Designer role on the Fintech team. Payment experiences are among the most consequential a person has: getting paid, sending money, managing finances. They have to work correctly and clearly for everyone, every time. That is the kind of design problem I want to be close to.}

\lettercontent{I have spent 15 years designing for high-traffic, multi-market consumer products, building the design systems and small teams that keep the work consistent as products grow. Most of my career has been B2C at scale, and I lead by doing the work alongside the team, not by directing from a distance. What I would bring:}

{\raggedright\fontspec{Fira Sans}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Consumer product at scale:} I have designed for products used by millions of users across multiple markets and currencies, with real pressure on every flow to perform. That is close to what the Fintech team does.
    \item \textbf{Design systems across surfaces:} I build token-based component libraries, with handoff that engineers actually use. One of them cut development time by 30\% and later ran across 10+ websites.
    \item \textbf{Evidence-based decisions:} I run A/B tests, use VWO and HotJar to measure flows, and base design decisions on data. Payment flows live or die on this.
    \item \textbf{Design leadership by doing:} I led a cross-functional design team of seven, including two team leads, owning design strategy from direction to shipped product. I hold the bar while doing the work myself.
    \item \textbf{AI-augmented delivery:} Claude Code is part of how I deliver, not a side experiment. I built a Figma-to-development pipeline that turns design tokens into production templates, and I ship working prototypes the team builds on.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{I do not have a fintech background, and the posting is clear that it is a plus, not a requirement. What I do have is 15 years of consumer product design at the kind of scale where getting flows right matters, and a design-systems foundation that makes it possible to move fast without breaking consistency.}

\lettercontent{I am based in Belgrade and available to start without any visa or relocation delays. I would like to talk about the Fintech team and what you are building.}

\begin{flushright}
\closing{Kind regards,}

\signature{Marko Rosić}
\end{flushright}
\end{document}
